\begin{document}
\chapter{Introduction of The Project}
\section{Tourism and Information Technology}
\paragraph{}
One of the most important part of the economic growth of Thailand is " Tourism ". It provides our country much money that it becomes one of the main income of Thailand. Having brilliant natural resources, kind people, beautiful attraction and good culture are main characteristics of Thailand.
\paragraph{}
    During the stay of tourists, one important part of the stay is the accommodation. There are several choices of accommodation which could be hotel, homestay, resort or even a bangalore. Those accommodations need one same thing is management system.
 \paragraph{}
    Since we are moving into the World of Information Technology(IT) , developing a management system for hotel(or any relating accommodations) will be needed to oriented in Information and Technology also. Developing the system and using the idea of IT could bring much more efficiency of resources and generate more income to the hotel. That is why we believe that a good Hotel Management System is very important to any accommodation business anywhere, especially Thailand.

\section{Hotel Management System}
\paragraph{}
Managing a hotel does not include only booking a room for a guest, but it include so many more tasks which are complicating and hideous job to do manually. This is where Management System will handle the complex part and allow mans to work more efficiently.
\paragraph{}
 Hotel Management System is expertise in management , professional managers, technicians, manuals, systems, etc. On the basis of management fees and share of profits as incentive payment , leading to the prosperity and profit for the hotel.
 \paragraph{}
 Our hotel management system will include
\begin{enumerate}
	\item Hotel Information
	\begin{enumerate}
		\item Information about hotel/picture
		\item Facilities
		\item Rooms
	\end{enumerate}

	\item Customer System
	\begin{enumerate}
		\item register/login system
		\item view/edit profile information
		\item booking system
		\item request to hotel
		\item payment
		\item view the message from admin
	\end{enumerate}

	\item Hotel Administration System
	\begin{enumerate}
	 	\item login system
    		\item staff and customer profile
    		\item view customer booking
 		\item room management
    		\item message to customer
    		\item payment system
		\item charge money from customers
	\end{enumerate}
\end{enumerate}
\paragraph{}
    And will be demonstrated later in this report.
\paragraph{}
    The term of Hotel Management System includes the management of each and every aspect related to the hotel for the attraction.Smoothness of handling things and proper management such as Booking system , Payment system , Registrations system.The better service can make more attraction for tourist and can make more the profit not only to the hotel but also indirectly to the country.
\section{What is a good Hotel Management System?}
\paragraph{}
     A good Hotel Management System is the system that should be comprehensive of necessary functions that can provide a high quality of service for customer. Also it must allows staffs to use the system efficiently. In other words, the system must accomplish both usability goals and user experience goals.
\section{Database}
\paragraph{}
    A database is a collection of information organized to provide efficient retrieval. The collected information could be in any number of formats (electronic, printed, graphic, audio, statistical, combinations). There are physical (paper/print) and electronic databases.
A database could be as simple as an alphabetical arrangement of names in an address book or as complex as a database that provides information in a combination of formats.
\paragraph{}
   Database can generally be looked at as being a collection of records, each of which contains one or more fields (i.e., pieces of data) about some entity (i.e., object), such as a person, organization, city, product, work of art, recipe, chemical, or sequence of DNA. For example, the fields for a database that is about people who work for a specific company might include the name, employee identification number, address, telephone number, date employment started, position and salary for each worker.
\section{Database and Hotel Management System}
\paragraph{}
	By taking advantage of database system we could use it to create complex system for hotel management such as manipulating payments from customer or managing room. Thus running a business of hotel will definitely use database system which will be later demonstrated in this project. Hotel Management System will need a database because to store records such as staff or customers profile, facilities information ,payment records, etc.Also these things which has relation together is a good way because we could use the functions of MySQL to manipulate them.
\section{Hotel Management System : CU@MyPlace}
\paragraph{}
    Our project will create the system of Hotel Management that is capable of handling customers actions and staff actions.
\paragraph{}
	Firstly, the project will include a website that has information of a hotel. We developed it using HTML and CSS. Then the website will brings customer to the booking area which allows user to pick a room and date, then pay for the selection and print confirmation for visiting the hotel.
\paragraph{}
	Second, the customers will have their system for viewing or modifying bookings. They also capable of sending request tickets to hotel for some special preparation.
\paragraph{}
	Third, the administration system will allows staffs to do hotel management duties such as seeing booking, managing status of rooms or contacting customers.


\end{document}
